---
title: "Project-2"
author: "Vito Založnik"
date: "13 12 2021"
output: pdf_document
---

## Setup
In this block are needed libraries for work. Workdir is set to my folder on my computer. For running this notebook I used  R version 4.1.2. All work is done here, except figure 1 was done in seperate script called Plot1.R. First data preprocesing (editing some .csv lines that pandas and R could not load) is in added jupyter notebook.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Set working dir
setwd("C:/Users/zaloz/Desktop/exFMF/upd/project-2-databox-ZaloznikV")

# Library installation.
if (!require("ggplot2")) install.packages("ggplot2");
if (!require("tidyverse")) install.packages("tidyverse");
if (!require("ggcorrplot")) install.packages("ggcorrplot");

# Load required libraries.
library(ggplot2);
library(tidyverse);
library(ggcorrplot);

```

## First look at data.
Firts lets look at data and remove some column names patterns that are anoying to write.
```{r}
df <- read.csv("signups/SignupsAttributes.csv")
#summary(df)

df

df %>% 
  rename_with(~str_remove(., "X.")) -> df
df %>%
  rename_with(~str_remove(., "properties.")) -> df
df %>%
  rename_with(~str_remove(., "_company")) -> df


agency <- select(df, c("is_agency"))
count(agency, is_agency) %>%
  mutate_at(vars(n), ~ ./nrow(agency))
```

We can see, that most of users are not agencies.

```{r}


df %>%
  group_by(country) %>%
  count -> country_agency #median only 9, mean 188, a lot of difference in use by country.
#lets look at only highest countries to see what are their properties. 
summary(country_agency$n)
treshold <- quantile(country_agency$n, 0.75)


ggplot(country_agency[which(country_agency$n>treshold),],aes(x=reorder(country,-n), y=n)) + 
  #scale_y_continuous(trans='log2') + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_bar(stat="identity")


a <- country_agency[which(country_agency$n>treshold),]
b <- a$country
c <- as.array(b)

plt2 <- df[which(df$country %in% c),] #look only at top 75% of countries 

plt2 %>% 
  group_by(country, is_agency ) %>%
  count -> plt2

ggplot(plt2, aes(x=reorder(country, -n), y=n, colour = is_agency)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_bar(stat="identity")  + 
  xlab("Country name") + ylab("Number of companies")  +
  ggtitle("Number of distinque customers by country and status") 

ggsave(
  "nbr_companies_country.png",
  plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 2,
  width = NA,
  height = NA,
  units = c("in", "cm", "mm", "px"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL
)

```
It is interesting, there is just few countries who has majority of customers. Median is 18 customers per country but mean is 331. This mean there is a lot of outliers. 
## Changing some data classes for easier further analysys
```{r}
df[df == "undefined"] <- NA
df[df == "true"] <- TRUE
df[df== "false"] <- FALSE
df
df$is_agency <- as.logical(df$is_agency)
df$had_trial <- as.logical(df$had_trial)
df$is_activated <- as.logical(df$is_activated)
df$has_mobile <- as.logical(df$has_mobile)
df$level_achieved <- as.numeric(df$level_achieved)
df

#la <- df[which(!is.na(df$level_achieved)),]
#la
#cor(la$is_activated, la$level_achieved)




```

Lets focus on those who are paying or not and try to find some features of them.
```{r}
#paying <- df[which(!is.na(df$became_paying)),]
#paying
#change data at became_paying, became_pql, canceled, trial_feature(change to number)

paying <- df
paying
time_series <- paying
paying$became_paying[!is.na(paying$became_paying)] <- 1
paying$became_pql[!is.na(paying$became_pql)] <- 1
paying$cancelled[!is.na(paying$cancelled)] <- 1
paying
paying$became_paying[is.na(paying$became_paying)] <- 0
paying$became_pql[is.na(paying$became_pql)] <- 0
paying$cancelled[is.na(paying$cancelled)] <- 0

paying$trial_features <- str_count(paying$trial_features,coll(";")) + 1
paying$trial_features[is.na(paying$trial_features)] <- 0

paying$became_paying <- as.numeric(paying$became_paying)
paying$became_pql <- as.numeric(paying$became_pql)
paying$cancelled <- as.numeric(paying$cancelled)

names = c("is_agency", "became_paying", "became_pql", "cancelled", "had_trial", "trial_features", "is_activated")

corr <- cor(paying[names])
ggcorrplot(corr, hc.order = TRUE, type = "lower",
   lab = TRUE)

ggsave(
  "corr.png",
  plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 2,
  width = NA,
  height = NA,
  units = c("in", "cm", "mm", "px"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL
)

df
  

```

```{r pressure, echo=FALSE}
plot(pressure)
```
```{r} 
#part of paying and pql by country

paying_mean <- paying[c("country", "became_paying", "became_pql")]
 
paying_mean %>%
	group_by(country) %>%
	summarise(became_paying = n()) -> P


paying_mean <- aggregate(paying_mean[, 2:3], list(paying_mean$country), mean)
colnames(P) <- c("C", "sum")
paying_mean$sum <- P$sum
# Everything on the same plot by country
ggplot(paying_mean, aes(x = became_paying, y=became_pql, color= sum)) + 
  geom_point() + scale_color_gradientn(colors = rainbow(5))+
  theme_bw() +
  geom_smooth(method = "loess", SE=TRUE) + 
  ggtitle("Ratio of companies by country and amount ") 

ggsave(
  "ratio_paye_pql_county.png",
  plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 2,
  width = NA,
  height = NA,
  units = c("in", "cm", "mm", "px"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL
)

```
```{r}
#lets look more close trials in those who became baying, will work more on it in python
t_s <- time_series[which(!is.na(time_series$became_paying)),]
t_s <- t_s[which(!is.na(t_s$trial_features)),]
t_s <- t_s[which(t_s$trial_features != ""),]


write.csv(t_s$trial_features, "trial_features.csv")
### GO TO JUPYTER NOTEBOOK VISUALIZATION 2!

### BACK FROM JUPYTER NOTEBOOK

t_s_2 <- read.csv("trial_features_2.csv")
t_s_2 <- t_s_2$X0
table(t_s_2)

p2 <- as.data.frame(table(t_s_2))


df[which(is.na(df$became_paying)),]
n_t_s <- df[which(is.na(df$became_paying)),]
n_t_s <- n_t_s[which(n_t_s$trial_features != ""),]
write.csv(n_t_s$trial_features, "n_t_s.csv")

d <- read.csv("n_trial_features_2.csv")
d <- d$X0
d <- as.data.frame(table(d))
d$Freq <- d$Freq / sum(d$Freq)
p2$Freq <- p2$Freq / sum(p2$Freq)
p2$not_payed <- d$Freq

p2 %>% arrange(desc(Freq)) -> p2
colnames(p2) <- c("t_s_2", "become_payed", "not_become_payed")

p2 <- melt(p2, id.vars='t_s_2')

ggplot(p2, aes(x= t_s_2, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  xlab("Feature name") + ylab("Ratio") +
   ggtitle("Probability density of features used by payed status") 

ggsave(
  "density_deatures.png",
  plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 2,
  width = NA,
  height = NA,
  units = c("in", "cm", "mm", "px"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL
)





```
```{r}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
